Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-12 Grassmannian_cells.tex
Reorganization in Section 3.1, more needed

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}\label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are exact for any $n\ge0$ and none of these representations contain preinjective direct summands.
      %Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
      %This is because $\Sigma_2 S_2=0$.
  \end{enumerate}
\end{remark}
We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
For a dimension vector $d\in\NN^{Q_0}$, write $R_d(K(n))$ for the affine space of representations of dimension $d$.
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  %\sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
   % \item The action of $\GL_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.

@@

  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
  Thus the roots $d(m,r)$ are also Schur roots.
  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite{sch}.
  This shows the second statement.

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{lemma}
\begin{proof}
  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.\sayT{The proof as written seems to be false as $\Hom(X,P_\ell)\ne0$ does not imply $\Hom(Y,P_\ell)\neq 0$ for all direct summands $Y$ of $X$. The easiest way would be to reorganize 3.8-3.10 in such way that we can assume that $X=P_m^V$ is indecomposable.} Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{proof}

\begin{lemma}
  \label{le:unique morphisms}
  There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
\end{lemma}
\begin{proof}
  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
\end{proof}

\begin{corollary}
  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable. Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable. The second part follows from Proposition \ref{pro:indecomposables} together with Lemma \ref{le:unique morphisms}.
\end{proof}

@@

\begin{lemma}
  \label{le:truncated homomorphisms}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$.
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}.\]
  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the result follows.
\end{proof}

\begin{corollary}\sayT{exchange $W$ and $V$?}
    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}

@@

  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:basic homological properties}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
\end{proof}
\begin{remark}
  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension-one subspace $V\subset H_m$ containing $W$.
  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
\end{remark}
\begin{corollary}
  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
  The result immediately follows from this.
\end{proof}
\begin{remark}
  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
\end{remark}

>>>>

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are exact for any $n\ge0$ and none of these representations contain preinjective direct summands.
      %Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
      %This is because $\Sigma_2 S_2=0$.
  \end{enumerate}
\end{remark}
We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
For a dimension vector $d\in\NN^{Q_0}$, write $R_d(K(n))$ for the affine space of representations of dimension $d$.
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  %\sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
   % \item The action of $\GL_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.

@@

  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
  Thus the roots $d(m,r)$ are also Schur roots.
  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite{sch}.
  This shows the second statement.

@@

\begin{lemma}
  \label{le:truncated homomorphisms}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$ and $\Ext(P_m,P_{m+1}^V=0$.
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}\]
  and a surjective map
  \[\Ext(P_m,P_{m+1})\onto\Ext(P_m,P_{m+1}^V).\]
  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the first claim follows.
  The final claim follows from Remark~\ref{rem:reflection recursion}.
\end{proof}

\begin{lemma}
  \label{le:unique preprojective morphism}
  For $V\in Gr(H_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
  Moreover, $\Ext(P_{m+1},P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives}, we obtain an isomorphism 
  \[\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)\]
  and a surjective map
  \[\Ext(P_{m+1},P_{m+1})\onto\Ext(P_{m+1},P_{m+1}^V).\]
  The identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$ under the isomorphism.
  The rigidity of $P_{m+1}$ gives the final claim.
\end{proof}

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in Gr(H_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(H_m/V)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
  In this case, there is an isomorphism 
  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}

\begin{corollary}
  \label{cor:indecomposable truncated} 
  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
  Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
  The second part follows from Proposition \ref{pro:indecomposables} together with Lemma \ref{le:unique morphisms}.
\end{proof}

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
\end{lemma}
\begin{proof}
  Recall that $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$).
  whereas $P_{m+1}^V$ is not preprojective.\sayT{The proof as written seems to be false as $\Hom(X,P_\ell)\ne0$ does not imply $\Hom(Y,P_\ell)\neq 0$ for all direct summands $Y$ of $X$. The easiest way would be to reorganize 3.8-3.10 in such way that we can assume that $X=P_m^V$ is indecomposable.}
  Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
\end{proof}

@@

@@

  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:unique preprojective morphism}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
\end{proof}
\begin{remark}
  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension-one subspace $V\subset H_m$ containing $W$.
  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
\end{remark}
\begin{corollary}
  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
  The result immediately follows from this.
\end{proof}
\begin{remark}
  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
\end{remark}
